---
title: "Merging code"
output: html_notebook
---

This code merges in the social rescreening data and the main data

```{r}
rm(list=ls())
newdata <- "./data/screeningSocialData-ErrorsToReScreen.rData"
olddata <- "./data/screeningSocialData.rData"
```

```{r}
load(newdata)
newdata <- data_bib
rm(data_bib)
```

```{r}
load(olddata)
olddata <- data_bib
rm(data_bib)
```

# Check

OK now check that the two don't overlap

```{r}
newdata$TI[2] %in% olddata$TI
```

They do overlap.  So we need to remove the old data rows with those in.

```{r}
counter <- which(olddata$TI %in% newdata$TI)
length(counter)
```

Now make a new data.frame with just the old screening data

```{r}
justold <- olddata[-counter,]
```

and make a new column to say the old data was not assessed in the final screen

```{r}
justold$Screen3_Assessed_v2 <- FALSE
```

Check the column names are the same

```{r}
names(justold) == names(newdata)
```

and add onto the end

```{r}
finaldata <- rbind(justold,newdata)
```


and save as both an .RData file AND a .csv

```{r}
write.csv(finaldata,"./data/FINAL_ScreenedData_20210511.csv",row.names=FALSE,quote=FALSE)
```

```{r}
save(finaldata,file="./data/FINAL_ScreenedData_20210511.rData")
```
