---
title: "Core analysis code"
author: "Miriam and Helen"
date: "6/24/2020"
output: html_document
---



```{r}
# Load the data and the core directory locations.  This will automatically work things out from globalvariables file.
# Use file.choose() to find the 0_GlobalVariables_Functions.R.  Copy/paste the EXACT address and location in here

address <- "~/Documents/GitHub/systematic-review-flash-floods/code/0_GlobalVariables_Functions.R"
source(address)

```


```{r}
# Separate out the papers into our groupings
bib_all <- data_bib; rm(data_bib)
bib_accept    <- bib_all[which(bib_all$Screen2_Reject == FALSE),]
bib_event     <- bib_all[which(bib_all$Screen2_Event == TRUE),]
bib_social    <- bib_all[which(bib_all$Screen2_Social == TRUE),]
bib_hydrology <- bib_all[which(bib_all$Screen2_Model == TRUE),]
bib_precip    <- bib_all[which(bib_all$Screen2_Precip == TRUE),]

```



# Plotting maps of locations

This code works for the author countries.  These maps aren't really interesting, but I can use this as a baseline to focus on locations for events and in the abstracts.

Useful resources

 - https://mgimond.github.io/Spatial/mapping-data-in-r.html
 - http://mazamascience.com/WorkingWithData/?p=1494
 - https://stackoverflow.com/questions/40119722/r-spplot-labels-in-wrong-places
 - https://stackoverflow.com/questions/3650636/how-to-attach-a-simple-data-frame-to-a-spatialpolygondataframe-in-r/3652472#3652472
 

## Function. Can be moved,
```{r}
Author_location <- function(data_bib,shapefile, plottitle){
   data_bib <- bib_all
   shapefile <- global_shape
   
   require(rgdal)
   require(tmap) 
   require(bibliometrix)
   
   #----------------------------------------------------------------------
   ## Get the countries of authors of from databib
   #----------------------------------------------------------------------
   M <- metaTagExtraction(data_bib, Field = "AU_CO", sep = ";")
   Countries <- as.data.frame(table(unlist(unlist(lapply(as.list(M$AU_CO),strsplit,";")))))
   names(Countries) <- c("CNTRY_NAME","AUTHOR")
   Countries$CNTRY_NAME <- as.character(Countries$CNTRY_NAME)

   #----------------------------------------------------------------------
   # Correct any differently spelt names
   #----------------------------------------------------------------------
   #wrongnames <- merge(shapefile@data,Countries,by="CNTRY_NAME",all.x=FALSE,all.y=TRUE)[which(is.na(merge(shapefile@data,Countries,by="CNTRY_NAME",all.x=FALSE,all.y=TRUE)$OBJECTID)==TRUE),]
   Countries$CNTRY_NAME[which(Countries$CNTRY_NAME %in% "KOREA")] <- "SOUTH KOREA"
   Countries$CNTRY_NAME[which(Countries$CNTRY_NAME %in% "MYANMAR")] <- "MYANMAR (BURMA)"
   Countries$CNTRY_NAME[which(Countries$CNTRY_NAME %in% "TANZANIA")] <- "TANZANIA, UNITED REPUBLIC OF"
   Countries$CNTRY_NAME[which(Countries$CNTRY_NAME %in% "U ARAB EMIRATES")] <- "UNITED ARAB EMIRATES"  
   Countries$CNTRY_NAME[which(Countries$CNTRY_NAME %in% "USA")] <- "UNITED STATES" 

   #----------------------------------------------------------------------
   # Merge the author list into the shapefile
   # help : https://stackoverflow.com/questions/40119722/r-spplot-labels-in-wrong-places
   # https://stackoverflow.com/questions/3650636/how-to-attach-a-simple-data-frame-to-a-spatialpolygondataframe-in-r/3652472#3652472
   #----------------------------------------------------------------------
   shapefile@data$CNTRY_NAME <- toupper(shapefile@data$CNTRY_NAME)
   shapefile@data = data.frame(shapefile@data, Countries[match(shapefile@data[,"CNTRY_NAME"], Countries[,"CNTRY_NAME"]),])
   shapefile@data$AUTHOR[is.na(shapefile@data$AUTHOR)==TRUE] <- 0 

   #----------------------------------------------------------------------
   ## make a clever log10 scale
   #----------------------------------------------------------------------
   counter <- c(1,10,50,100,500,1000,5000,10000)
   colscale <- c(0)
   n <- 1
   while(counter[n] < max(shapefile@data$AUTHOR,na.rm=TRUE)){
      colscale <- c(colscale,counter[n])
      n <- n+1
   }
   colscale <- c(colscale,ceiling(max(shapefile@data$AUTHOR,na.rm=TRUE)/100) * 100)

   #----------------------------------------------------------------------
   # plot onto global grid
   #----------------------------------------------------------------------
   outputplot <- tm_shape(shapefile) + 
                 tm_polygons(col="AUTHOR",palette="PuBuGn",
                             border.col = "black",lwd=.5,border.alpha = .5, 
                             style="cont",breaks=colscale,
                             title = "Number of papers") +
                 tm_legend(outside = TRUE,main.title=plottitle)
   
   return(outputplot)
}   
```   
   
   
## Running the function

```{r}

print(Author_location(bib_all,global_shape,"All papers screened"))

print(Author_location(bib_accept,global_shape,"Accepted through screening papers"))

print(Author_location(bib_event,global_shape,"Papers about a specific event"))

print(Author_location(bib_social,global_shape,"Socially tagged papers"))

print(Author_location(bib_hydrology,global_shape,"Hydrology tagged papers"))

print(Author_location(bib_precip,global_shape,"Precip tagged papers"))

```

## Text Analysis

```{r}

# Create keyword co-occurrences network
NetMatrix <- biblioNetwork(bib_accept, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```

```{r}
library(ggplot2)
library(reshape2)

words <- KeywordGrowth(bib_accept, Tag = "ID", sep = ";", top = 10, cdf = TRUE)

wordsReshaped <- t(words)

#ggplot(words, aes(x = words$Year, y = words$)) + geom_tile()

```

## Bibliometrix Summary Information

```{r}
results <- biblioAnalysis(bib_accept, sep = ";")
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
plot(x = results, k = 10, pause = FALSE)

```

## Exporting DOIs

In order to look at the full text, we wanted to pull a selection of papers into a reference management software like Zotero. 
The easiest way we found, was to create a CSV of the selected DOIs and copy that into the reference manager. 
```{r}

# write.csv(bib_all$DI, "exports/DOIs-all.csv", row.names = data_bib$TI)
social_data_bib <- data_bib[data_bib$Screen2_Social == TRUE, ]
write.csv(bib_social$DI, "exports/DOIs-social.csv", row.names = social_data_bib$TI)

```



